### 2025-02-14 chapters/LBM_technique.tex
Changes 1. Made tex files human readable again 2. Added content to paper3 tex file 3. Added licenses to some of the images from other papers

\begin{figure}[h]
    \centering
    \includegraphics[scale = 0.7]{figures/methods/d3q19_lattice.jpg}
    \caption{D3Q19 lattice demonstrating the rest, nearest and next nearest direction that correspond to the 19 directions $(i)$ of the lattice with lattice velocity $c_{i}$.}
    \label{fig:d3q19_lattice}
\end{figure}

@@

\begin{equation}
    \mathbf{F}_{ij} = \frac{3 \mu_0}{4 \pi} [\frac{5(m_i \cdot \mathbf{r}_{ij})(m_j \cdot \mathbf{r}_{ij})}{|\mathbf{r}_{ij}|^7}\mathbf{r}_{ij} - \frac{(m_i \cdot m_{j})\mathbf{r}_{ij} + (m_i \cdot \mathbf{r}_{ij})m_i + (m_j \cdot \mathbf{r}_{ij})m_j }{|\mathbf{r}_{ij}|^5})]
\label{eq:dipole_magnetic_force}
\end{equation}

\begin{equation}
    \mathbf{T}_{ij} = \frac{\mu_0}{4 \pi}[ \frac{3(m_j \cdot \mathbf{r}_{ij})m_i \times \mathbf{r}_{ij} }{|\mathbf{r}_{ij}|^5} - \frac{m_i \cdot m_j }{|\mathbf{r}_{ij}|^3} ]
    \label{eq:dipole_magnetic_torque}
\end{equation}

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[scale = 0.7]{figures/methods/d3q19_lattice.jpg}
    \caption{D3Q19 lattice demonstrating the rest, nearest and next nearest direction that correspond to the 19 
    directions $(i)$ of the lattice with lattice velocity $c_{i}$. \cite{schmieschek_lb3d_2017} Reproduced from 
    Schmieschek et al. under the Creative Commons license.}
    \label{fig:d3q19_lattice}
\end{figure}

@@

\begin{equation}
    \mathbf{F}_{ij} = \frac{3 \mu_0}{4 \pi} [\frac{5(m_i \cdot \mathbf{r}_{ij})(m_j 
    \cdot \mathbf{r}_{ij})}{|\mathbf{r}_{ij}|^7}\mathbf{r}_{ij} - \frac{(m_i \cdot m_{j})\mathbf{r}_{ij} + 
    (m_i \cdot \mathbf{r}_{ij})m_i + (m_j \cdot \mathbf{r}_{ij})m_j }{|\mathbf{r}_{ij}|^5}]
\label{eq:dipole_magnetic_force}
\end{equation}

\begin{equation}
    \mathbf{T}_{ij} = \frac{\mu_0}{4 \pi}[ \frac{3(m_j \cdot \mathbf{r}_{ij})m_i \times \mathbf{r}_{ij} }
    {|\mathbf{r}_{ij}|^5} - \frac{m_i \cdot m_j }{|\mathbf{r}_{ij}|^3} ]
    \label{eq:dipole_magnetic_torque}
\end{equation}

### 2025-02-14 chapters/introduction.tex
Changes 1. Made tex files human readable again 2. Added content to paper3 tex file 3. Added licenses to some of the images from other papers

These range from Metal Organic Framework(MOF) enhanced gas adsorption, \textcolor{blue}{https://doi.org/10.1002/admi.201400040} This increased surface area to volume ratio enhances the properties of the base material in applications such as catalysis, battery electrodes and drug delivery systems among many more making them valuable microstructures. \cite{cha_bicontinuous_2019, samdani_bicontinuous_2017, thorson_bijel-templated_2019}

\begin{figure}
    \centering
    \includegraphics[scale = 0.5]{figures/introduction/bijel_templating.png}
    \caption{Fabrication of a graphite oxide battery electrode using bijel template. \cite{garcia_scalable_2019}}
    \label{fig:bijel_template}
\end{figure}

Conventionally, porous materials have been synthesized through solvothermal synthesis or pyrolysis used in the synthesis of zeolites and activated carbon respectively. With more targeted applications of porous materials, synthesis techniques such as sol-gel synthesis, freeze drying and various forms of templating have been utilized to synthesize porous materials from length scales of $10^{-9}m$ to $10^{-3}m$. \cite{stein_morphological_2008, ray_comprehensive_2016, cervellere_mesoscopic_2019, garcia-bennett_unique_2020, zhang_emulsion_2019, alves-rosa_design_2013} Industry has also taken up techniques such as electrospinning to generate non woven fibers, used in membrane synthesis. Templating techniques in particular offer access to various pore length scales, bottom up synthesis and functionality through leveraging various physical phenomena. Colloidal templating works through the close packing of particles. Surfactant and polymer templating work through the assembly of macromolecules into their equilibrium configurations. Emulsion templating utilizes the phase separation of partially misicble liquids to form the pore structure of a porous material.

Emulsion templating offers access to a large length scale of tunable pore sizes, continous production through microfluidic junctions or other flow media, functionalization through the addition of additives or stabilizers, scope of accessible microstructures and mild synthesis conditions. It can further be extended to include heirarchical porosity, further enhancing its utility and fabricated material properties. \cite{yang_hierarchically_2017, thompson_hierarchically_2019, wang_morphology_2023} Figure \ref{fig:bijel_template} demonstrates how emulsion templating allows bottom up synthesis of hierarchically porous materials, although other examples do exist. \cite{garcia_scalable_2019, santiago_cordoba_aerobijels_2020, thorson_bijel-templated_2019, lu_controllable_2020, wang_morphology_2023}

\begin{figure}
    \centering
    \includegraphics[scale = 0.3]{figures/introduction/bijel_coarsening.jpg}
    \caption{Initiation and arrest of spinodal decomposition as particles adsorb onto the interface, followed by jamming once the interfacial area matches the cross sectional area of the adsorbed particles\cite{stratford_colloidal_2005}}
    \label{fig:bijel_coarsen}
\end{figure}

@@

Bijels were discovered in simulations in 2005 and experimentally realized in 2007 when a mixture of water and 2-6-lutidine mixed with surface modified silica nanoparticles underwent thermally induced spinodal decomposition. \cite{stratford_colloidal_2005, herzig_bicontinuous_2007} Since then, multiple other casting mixtures and particle chemistry's have been used to fabricate bijels using Thermally Induced Spinodal Decomposition (TIPS). \cite{lee_bicontinuous_2010, bai_dynamics_2015} More recently, techniques such as Solvent Transfer Induced Phase Separation (STrIPS), Vapor Induced Phase Separation (VIPS), Non-solvent Induced Phase Separation (NIPS), homogenization and liquid in liquid printing have been utilized to fabricate bijels, demonstrating the ability for bijels to be synthesized in a continuous process, suitable for scale up. \cite{haase_continuous_2015, wang_scalable_2020, cai_bijels_2017, yabuno_preparation_2020, wang_bicontinuous_2023, amirfattahi_fabrication_2024} These techniques also offer preparation of bijels in various different shapes and form-factors for various uses such as fibers, coatings and capsules, seen in Figure \ref{fig:strips}. \cite{haase_continuous_2015, boakye-ansah_controlling_2020, kharal_hightensile_2020, wang_bicontinuous_2023}

\begin{figure}[h]
    \centering
    \includegraphics[scale = 2]{figures/literature_review/STRIPPS.jpg}
    \caption{STrIPS in action. Extrusion of the bijel casting mixture into a non-solvent bath, followed by removal of solvent from the casting mixture through diffusion. \cite{haase_continuous_2015}}
    \label{fig:strips}
\end{figure}

>>>>

These range from Metal Organic Framework(MOF) enhanced gas adsorption, \textcolor{blue}{https://doi.org/10.1002/admi.201400040} 
This increased surface area to volume ratio enhances the properties of the base material in applications such as catalysis, 
battery electrodes and drug delivery systems among many more making them valuable microstructures. \
cite{cha_bicontinuous_2019, samdani_bicontinuous_2017, thorson_bijel-templated_2019}

\begin{figure}
    \centering
    \includegraphics[scale = 0.5]{figures/introduction/bijel_templating.png}
    \caption{Fabrication of a graphite oxide battery electrode using bijel template. Reproduced from Garcie et al. under license number 1548092-1. \cite{garcia_scalable_2019}}
    \label{fig:bijel_template}
\end{figure}

Conventionally, porous materials have been synthesized through solvothermal synthesis or pyrolysis used in the synthesis of zeolites and 
activated carbon respectively. With more targeted applications of porous materials, synthesis techniques such as sol-gel synthesis, 
freeze drying and various forms of templating have been utilized to synthesize porous materials from length scales of $10^{-9}m$ to 
$10^{-3}m$. \cite{stein_morphological_2008, ray_comprehensive_2016, cervellere_mesoscopic_2019, garcia-bennett_unique_2020, zhang_emulsion_2019, 
alves-rosa_design_2013} Industry has also taken up techniques such as electrospinning to generate non woven fibers, used in membrane synthesis. 
Templating techniques in particular offer access to various pore length scales, bottom up synthesis and functionality through leveraging various 
physical phenomena. Colloidal templating works through the close packing of particles. Surfactant and polymer templating work through the 
assembly of macromolecules into their equilibrium configurations. Emulsion templating utilizes the phase separation of partially miscible 
liquids to form the pore structure of a porous material.

Emulsion templating offers access to a large length scale of tunable pore sizes, continuous production through microfluidic junctions or 
other flow media, functionalization through the addition of additives or stabilizers, scope of accessible microstructures and mild synthesis 
conditions. It can further be extended to include heirarchical porosity, further enhancing its utility and fabricated material properties. 
\cite{yang_hierarchically_2017, thompson_hierarchically_2019, wang_morphology_2023} Figure \ref{fig:bijel_template} demonstrates how emulsion 
templating allows bottom up synthesis of hierarchically porous materials, although other examples do exist. 
\cite{garcia_scalable_2019, santiago_cordoba_aerobijels_2020, thorson_bijel-templated_2019, lu_controllable_2020, wang_morphology_2023}

\begin{figure}
    \centering
    \includegraphics[scale = 0.3]{figures/introduction/bijel_coarsening.jpg}
    \caption{Initiation and arrest of spinodal decomposition as particles adsorb onto the interface, followed by jamming once the 
    interfacial area matches the cross sectional area of the adsorbed particles\cite{stratford_colloidal_2005}. Reproduced from Adhikari et al. 
    under license number 5966820525314.}
    \label{fig:bijel_coarsen}
\end{figure}

@@

Bijels were discovered in simulations in 2005 and experimentally realized in 2007 when a mixture of water and 2-6-lutidine mixed with 
surface modified silica nanoparticles underwent thermally induced spinodal decomposition. \cite{stratford_colloidal_2005, herzig_bicontinuous_2007}
Since then, multiple other casting mixtures and particle chemistry's have been used to fabricate bijels using Thermally Induced Spinodal 
Decomposition (TIPS). \cite{lee_bicontinuous_2010, bai_dynamics_2015} More recently, techniques such as Solvent Transfer Induced Phase 
Separation (STrIPS), Vapor Induced Phase Separation (VIPS), Non-solvent Induced Phase Separation (NIPS), homogenization and liquid in 
liquid printing have been utilized to fabricate bijels, demonstrating the ability for bijels to be synthesized in a continuous process, 
suitable for scale up. \cite{haase_continuous_2015, wang_scalable_2020, cai_bijels_2017, yabuno_preparation_2020, wang_bicontinuous_2023, 
amirfattahi_fabrication_2024} These techniques also offer preparation of bijels in various different shapes and form-factors for various 
uses such as fibers, coatings and capsules, seen in Figure \ref{fig:strips}. \cite{haase_continuous_2015, boakye-ansah_controlling_2020, 
kharal_hightensile_2020, wang_bicontinuous_2023}
\begin{figure}[h]
    \centering
    \includegraphics[scale = 2]{figures/literature_review/STRIPPS.jpg}
    \caption{STrIPS in action. Extrusion of the bijel casting mixture into a non-solvent bath, followed by removal of solvent from 
    the casting mixture through diffusion. Reproduced from Haase et al. 2015 under license number 5913140219015. \cite{haase_continuous_2015}}
    \label{fig:strips}
\end{figure}

### 2025-02-14 chapters/lit_review.tex
Changes 1. Made tex files human readable again 2. Added content to paper3 tex file 3. Added licenses to some of the images from other papers

After their discovery, interest in particle stabilized emulsions became minimal. However, increased interest in them has resurfaced since the 1980s owing to their applications in food science. One such example is fat crystals stabilizing water droplets in oil to create margarine. Particle stabilization has also been of interest owing to their lower toxicity and greater ease of sustainable sourcing.
It has been shown that chemical surfactants can be toxic to aquatic life, acting as a xeno-hormone and interfering with their reproduction. \textcolor{blue}{https://www.sciencedirect.com/science/article/pii/S0304389420302879, https://www.sciencedirect.com/science/article/pii/S014765131530172X} Additionally, particles based cellulose or chitin can be obtained from renewable sources. \textcolor{blue}{https://www.tandfonline.com/doi/full/10.1080/14686996.2017.1401423, 10.1021/acs.biomac.6b00144, 10.1021/acs.langmuir.7b03959} It has also been shown that particle stabilized emulsions are stable for long periods of time. These development have resulted in particle stabilized emulsions seeing a large increase in interest.

The microstructure properties of particle stabilized emulsions were explored in the early 2000s by Lumsdon and Binks among many others. They observed that the radius of emulsion droplets, $R_e \propto \frac{\phi_w}{\phi_p}$, where $\phi_w$ and $\phi_p$ are volume fractions of water and particles respectively. \cite{binks_pickering_2001} They also identified that there were other techniques to modify the microstructure of a Pickering Emulsion such as concentration of fluids and particle wettability. Neutrally wetting particles do not impart a preferential curvature to the interface. When using non-neutrally wetting particles, bridged droplets, capillary aggregates and other non droplet microstructures can be observed. Bijels, are synthesized in a system using equal volume fraction of fluids and neutrally wetting particles, thus facilitating the formation of tortuous, co-continuous domains.

Bijels themselves are synthesized in systems which have roughly equal fluid volume fractions and neutrally wetting particles so as to not impose preferential curvature on the interface. \cite{stratford_colloidal_2005, herzig_bicontinuous_2007, lee_bicontinuous_2010, jansen_bijels_2011, velankar_non-equilibrium_2015} Reeves et al. demonstrated that bijels stabilized with nanoparticles are more stable than those with microparticles due to better mechanical properties and interface coverage. \cite{reeves_particle-size_2015}  Additionally, research by Jansen, Harting, and Hijnen et al. showed that the bijel domain size $L \propto \frac{1}{\phi_p}$ for both rod-like and spherical particles. Although the pre-factor is dependent upon the particle geometry, this feature has been seen with many other particle shapes as well. \cite{hijnen_bijels_2015, madivala_exploiting_2009, gunther_timescales_2014, daware_emulsions_2015, loudet_capillary_2005, cheng_shape-anisotropic_2013}

@@

\begin{figure}
    \centering
    \includegraphics[scale = 0.5]{figures/literature_review/interfacial_curvature.png}
    \caption{Quadropolar capillary interactions around prolate ellipsoidal particles caused by interfacial deformations around the particle. \cite{loudet_capillary_2005}}
    \label{fig:anisotropic_particle_interface}
\end{figure}

>>>>

After their discovery, interest in particle stabilized emulsions became minimal. However, increased interest in them has resurfaced since the 1980s owing to 
their applications in food science. One such example is fat crystals stabilizing water droplets in oil to create margarine. Particle stabilization has also 
been of interest owing to their lower toxicity and greater ease of sustainable sourcing through the usage of cellulose or chitin particles. \
textcolor{blue}{https://www.tandfonline.com/doi/full/10.1080/14686996.2017.1401423, 10.1021/acs.biomac.6b00144, 10.1021/acs.langmuir.7b03959} 
Additionally, chemical surfactants can be toxic to aquatic life, acting as a xeno-hormone and interfering with their reproduction. 
\textcolor{blue}{https://www.sciencedirect.com/science/article/pii/S0304389420302879, https://www.sciencedirect.com/science/article/pii/S014765131530172X}

Compared to emulsions stabilized using surfactants, particle stabilized emulsions offer greater resistance to coarsening, resulting in increased interest in 
them once again. The microstructure properties of particle stabilized emulsions were explored in the early 2000s by Lumsdon and Binks among many others. They 
observed that the radius of emulsion droplets, $R_e \propto \frac{\phi_w}{\phi_p}$, where $\phi_w$ and $\phi_p$ are volume fractions of water and particles 
respectively. \cite{binks_pickering_2001} They also identified that there were other techniques to modify the microstructure of a Pickering Emulsion 
such as concentration of fluids and particle wettability. Neutrally wetting particles do not impart a preferential curvature to the interface. When 
using non-neutrally wetting particles, bridged droplets, capillary aggregates and other non droplet microstructures can be observed. Bijels, are synthesized 
in a system using equal volume fraction of fluids and neutrally wetting particles, thus facilitating the formation of tortuous, co-continuous domains.

Bijels are synthesized in systems which have roughly equal fluid volume fractions and neutrally wetting particles so as to not impose preferential 
curvature on the interface. \cite{stratford_colloidal_2005, herzig_bicontinuous_2007, lee_bicontinuous_2010, jansen_bijels_2011, velankar_non-equilibrium_2015} 
Reeves et al. demonstrated that bijels stabilized with nanoparticles are more stable than those with microparticles due to better mechanical properties and 
interface coverage. \cite{reeves_particle-size_2015}  Additionally, research by Jansen, Harting, and Hijnen et al. showed that the bijel domain size 
$L \propto \frac{1}{\phi_p}$ for both rod-like and spherical particles. Although the pre-factor is dependent upon the particle geometry, this feature 
has been seen with many other particle shapes as well. \cite{hijnen_bijels_2015, madivala_exploiting_2009, gunther_timescales_2014, daware_emulsions_2015, 
loudet_capillary_2005, cheng_shape-anisotropic_2013}

@@

\begin{figure}
    \centering
    \includegraphics[scale = 0.5]{figures/literature_review/interfacial_curvature.png}
    \caption{Quadropolar capillary interactions around prolate ellipsoidal particles caused by interfacial deformations around the particle. 
    \cite{loudet_capillary_2005} Reproduced from Loudet et al. with license number RNP/25/FEB/088185}
    \label{fig:anisotropic_particle_interface}
\end{figure}

### 2025-02-14 chapters/model_params.tex
Changes 1. Made tex files human readable again 2. Added content to paper3 tex file 3. Added licenses to some of the images from other papers

Critical parameters in this system include fluid density $\rho_f$, dynamic viscosity $\eta$, surface tension $\sigma$, length scale $L$, and applied magnetic field strength $B$. The dynamic viscosity and surface tension is determined by the relaxation time using the BGK collision operator, $\eta = \rho_f c_s^2(\tau - \frac{1}{2})$ and $g_{kk'}$ respectively. Dimensionless numbers derived from the Buckingham Pi theorem are the Reynolds number($Re = \frac{\rho u L}{\eta}$), Weber number ($We = \frac{\rho u^2 L}{\sigma}$), and magnetic bond number ($\Bar{B} = \frac{Bd}{\sigma A}$). Here, $u$ is velocity, $d$ is the particle's dipole moment, and $A$ is the particle's cross-sectional area. The system's velocity and length scale are set as the domain size and coarsening rate. Parameters for the fluid, particle, and non-ideal mixing model used in the simulations are summarized in Table \ref{table:model_params}.

>>>>

Critical parameters in this system include fluid density $\rho_f$, dynamic viscosity $\eta$, surface tension $\sigma$, 
length scale $L$, and applied magnetic field strength $B$. The dynamic viscosity and surface tension is determined 
by the relaxation time using the BGK collision operator, $\eta = \rho_f c_s^2(\tau - \frac{1}{2})$ and $g_{kk'}$ 
respectively. Dimensionless numbers derived from the Buckingham Pi theorem are the Reynolds number
($Re = \frac{\rho u L}{\eta}$), Weber number ($We = \frac{\rho u^2 L}{\sigma}$), and magnetic bond number 
($\Bar{B} = \frac{Bd}{\sigma A}$). Here, $u$ is velocity, $d$ is the particle's dipole moment, and $A$ is the 
particle's cross-sectional area. The system's velocity and length scale are set as the domain size and coarsening rate. 
Parameters for the fluid, particle, and non-ideal mixing model used in the simulations are summarized in Table 
\ref{table:model_params}.

### 2025-02-14 chapters/paper3.tex
Changes 1. Made tex files human readable again 2. Added content to paper3 tex file 3. Added licenses to some of the images from other papers

In many of the manufacturing techniques outlined for continuous bijel production such as STrIPS, the rheological properties are essential in ensuring that the casting mixture remains processable. However, past work with ferrofluids and magnetic emulsions have showed how the rheological properties vary drastically as a function of the field strength. Bijels themselves have complex rheological properties stemming from the removal of particles from the interface if too much shear is applied. Therefore, avenues of exploration here would be how the rheological properties of bijels change under the influence of fields in response to an applied shear. One of the questions that will be investigated in particular will be how shear changes the orientation of the particles on the interface, the interfacial coverage of particles and if there is anisotropy in the viscosity during the application of a field owing to the orientation of particles towards the field.

First, a shear capillary number is defined as $Ca_s = \frac{\eta_{f} \dot{\gamma} L_{1}}{\sigma}$ where $\dot{\gamma} = \frac{u_{LE}}{L_x}$ is the strain rate and $L_1$ is the average domain size. \cite{frijters_effects_2012, yang_capillary_2022} In the literature, $Ca_s$ has been between between 0.04 and 0.16. However, the box size in these simulations were smaller, meaning that these capillary number ranges would exceed the maximum mach number the model allows if this same range were used $(Ma \leq 0.03)$. To accommodate this limitation the largest capillary number used will be $Ca_s = 10^-5$ which correspond to a maximum of $Ma \approx 0.002$. $Ca_s = 10^-6,  10^-7$ will also be used to demonstrate how the bijels respond to shear of varying strengths. As all particles used have only hard-sphere type interactions, it is expected that the behaviour seen should mimic 2D colloidal glasses percolating in 3D space, akin to what Ching and Mohraz saw, with an additional dependence on -the direction of shear. This would predict the discovery of particle monolayer dependent elasticity and yield stress along with shear thinning behaviour as a function of strain rate.

@@

>>>>

While the microstructure and synthesis techniques for bijels have been explored in earnest, the rheology of bijels
has only recently seen an uptick in interest. Some interesting phenomena for bijels and shearing include the 
presence of monogels, made by remixing the phase separated liquid domains of the bijel while the electrostatic
interactions between particles maintains the structure of the particle monolayer. \textcolor{blue}{https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.103.255502}
This behavior is system specific, suggesting the fluid system plays a role in this behavior as well. \textcolor{blue}{https://doi.org/10.1002/adfm.201002562} 
\cite{bai_dynamics_2015} Investigations have identified that confined bijels under shear undergo elongation of
the domains in the direction of shear succeeded by particle detachment from the interface and eventual failure of the bijel. \cite{bonaccorso_shear_2020}
More recently, bijels have been identified to be 2D glasses percolating in 3D space, characterized through comparing the complex rheology of bijels against
colloidal gels made from silica particles with electrostatic interactions. \cite{ching_bijel_2022}

In many of the manufacturing techniques outlined for continuous bijel production such as STrIPS, the rheological properties are essential in ensuring that 
the casting mixture remains processable. \cite{haase_continuous_2015,haase_situ_2016} While particle stabilized emulsions have been shown to be shear thinning, 
our investigation into magnetically stimuli responsive bijels will modify the behavior of these systems due to the application of magnetic fields. Past work with 
ferrofluids and magnetic emulsions have showed how the rheological properties vary drastically as a function of the field strength due to the orientation of the 
particles. \textcolor{blue}{https://doi.org/10.1016/j.colsurfa.2012.06.026} The orientation of the particle to shear as well as the nematic order of particles 
can cause shear banding and a smaller effective viscosity owing to a smaller cross sectional area being presented to the direction of shear.

In this chapter, we probe the dynamics of bijels under constant and complex shear to understand how the application of magnetic fields onto bijels stabilized with
anisotropic particles. We define a shear capillary number $Ca_s = \frac{\eta_{f} \dot{\gamma} L_{1}}{\sigma}$ where $\dot{\gamma} = \frac{2u_{LE}}{L_x}$ is the
strain rate and $L_1$ is the average domain size. \cite{frijters_effects_2012, yang_capillary_2022} In the literature, $Ca_s$ has been between between 0.04 
and 0.16. However, the box size in these simulations were smaller, meaning that these capillary number ranges would exceed the 
maximum mach number the model allows if this same range were used $(Ma \leq 0.03)$. To accommodate this limitation the 
largest capillary number used will be $Ca_s = 10^-5$ which correspond to a maximum of $Ma \approx 0.002$. $Ca_s = 10^-6,  
10^-7$ will also be used to demonstrate how the bijels respond to shear of varying strengths. As all particles used 
have only hard-sphere type interactions, it is expected that the behaviour seen should mimic 2D colloidal glasses 
percolating in 3D space, akin to what Ching and Mohraz saw, with an additional dependence on -the direction of shear. 
This would predict the discovery of particle monolayer dependent elasticity and yield stress along with shear thinning 
behaviour as a function of strain rate.

@@

\textcolor{blue}{https://doi.org/10.1073/pnas.0812519106}

\begin{itemize}
    \item Shear banding analyzed through looking at change in particle velocity in the x direction
    \item Shear banding analyzed through looking at change in $Q_6$ in the x direction
    \item 
\end{itemize}
